---
title: "Project proposal"
author: "MMTR"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
```

## 1. Introduction
The study focused on the effect of heatwaves on coral reef fish. The study was conducted by Van Wert et al. and was published on July 15, 2024. The Hawkfish were collected in Mo'orea, French Polynesia in 2019 during the winter and 2022 during the summer. They studied how marine heatwaves impacted the performance and thermal tolerance of the arceye hawkfish, which is a tropical predatory fish. 
More specifically, the researchers used five treatments (27, 28, 29, 31, or 33°C) for one week to test hawkfish’s acclimation ability, which they measured by metabolic performance metrics, including maximum metabolic rate (MMR), standard metabolic rate (SMR), and costs of digestion (specific dynamic action, SDA), using custom-made respirometry chambers. A subset of fish and wild fish were tested for thermal tolerance using an acute cardiac thermal tolerance test. 
This dataset contains 75 cases and 22 variables.
For this project, our research question focuses on the negative effects of heatwaves on hawkfish to understand the greater effect of climate change on marine populations. Some questions include:
1. What threat do heatwaves pose to hawkfish?
2. Does the season (summer vs winter) have any effect on the fish’s energy?
3. What is the long-term impact of these heatwaves on the fish’s health and physiology?
4. Will warming ocean temperatures affect the size of future hawkfish populations?

## 2. Data

Text goes here. Place your data in the /data folder, and add dimensions and codebook to the README in that folder. Then print out the output of glimpse() or skim() of your data frame.

```{r}
heatwaves_coral_fish <- read_csv("../data/VanWert_etal_2023_hawkfish.csv")
glimpse(heatwaves_coral_fish)
```

## 3. Data analysis plan

Text goes here.
- What variables will you visualize to explore your research questions?
- Will there be any other data that you need to find to help with your research question?
- Very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. (You can add to these later as you work on your project.)
- The data visualization(s) that you believe will be useful in exploring your question(s). (You can update these later as you work on your project.)


```{r}
# Code goes here
# Code to calculate summary statistics
# Code for a visualization
```
