---
title: "Project memo"
author: "MMTR"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(viridisLite)
library(ggplot2)
```

## Data Clean Up Steps for Overall Data

### Step 1: Upload main dataset

```{r upload-data}
heatwaves_coral_fish <- read_csv("../data/VanWert_etal_2023_hawkfish.csv")
glimpse(heatwaves_coral_fish)
```

### Step 2: Change Variable Names

```{r rename-variables}
heatwaves_coral_fish_clean <- heatwaves_coral_fish |>
  rename(wet_mass = bw_g,
         total_length = tl_cm,
         standard_length = sl_cm,
         max_metabolic_rate = mmr_corrected,
         standard_metabolic_rate = smr_low10_all,
         absolute_aerobic_scope = aas_corrected,
         factorial_aerobic_scope = fas,
         SDA_coeff = sda_coeff,
         temp_of_arrhythmia = tarr,
         peak_max_heart_rate = fhmax_peak,
         temp_at_max_heart_rate = tpeak)
```

## Plots

### Plot 1: Boxplot: Heatwave treatment vs. maximum metabolic rate (MMR)


```{r treatment-vs-MMR}

heatwave_vs_mmr <- heatwaves_coral_fish_clean |>
  ggplot(aes(x = treatment_new, y = max_metabolic_rate)) +
  geom_boxplot(fill = "#6BAED6") +
  scale_x_discrete(labels = function(x) ifelse(x == "wild", "wild", paste0(x, "°C"))) +
  labs(
    title = "Maximum Metabolic Rate by Heatwave Treatment",
    subtitle = "“wild” is the control group (no heatwave)",
    x = "Treatment (Heatwave Temperature)",
    y = "Maximum Metabolic Rate (MMR)"
  )

# Save the plot
ggsave("fig_heatwave_boxplot.png", heatwave_vs_mmr, width = 7, height = 5)

```

### Plot 2: Scatter Plot: Body length vs. post-feeding energy use, colored by season

```{r scatter}

heatwaves_coral_fish |>
  ggplot(aes(x = tl_cm, y = SDA_integrated, color = season)) +
  geom_point(alpha = 0.8) +
  labs(
    title = "Body Length vs. SDA (by Season)",
    x = "Total Length (cm)",
    y = "SDA Integrated"
  )

# Save the plot
ggsave("fig_heatwave_boxplot.png", heatwave_vs_mmr, width = 7, height = 5)
```

#### Final Plot 1

```{r}

```


### Plot 2: _________

### Plot 3: ___________

Add more plot sections as needed. Each project should have at least 3 plots, but talk to me if you have fewer than 3.

### Plot 4: ___________ 

