---
title: "Project memo"
author: "MMTR"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## Data Clean Up Steps for Overall Data

### Step 1: Upload main dataset

```{r upload-data}
heatwaves_coral_fish <- read_csv("../data/VanWert_etal_2023_hawkfish.csv")
glimpse(heatwaves_coral_fish)
```

### Step 2: Change Variable Names

```{r rename-variables}
heatwaves_coral_fish <- heatwaves_coral_fish |>
  rename(wet_mass = bw_g,
         total_length = tl_cm,
         standard_length = sl_cm,
         corrected_max_metabolic_rate = mmr_corrected,
         standard_metabolic_rate = smr_low10_all,
         absolute_aerobic_scope = aas_corrected,
         factorial_aerobic_scope = fas,
         SDA_coeff = sda_coeff,
         temp_of_arrhythmia = tarr,
         peak_max_heart_rate = fhmax_peak,
         temp_at_max_heart_rate = tpeak)
```

## Plots

### ggsave example for saving plots

```{r starwars ggsave example}
p1 <- starwars |>
  filter(mass < 1000, 
         species %in% c("Human", "Cerean", "Pau'an", "Droid", "Gungan")) |>
  ggplot() +
  geom_point(aes(x = mass, 
                 y = height, 
                 color = species)) +
  labs(x = "Weight (kg)", 
       y = "Height (m)",
       color = "Species",
       title = "Weight and Height of Select Starwars Species",
       caption = paste("This data comes from the starwars api: https://swapi.py43.com"))


ggsave("example-starwars.png", width = 4, height = 4)

ggsave("example-starwars-wide.png", width = 6, height = 4)
```



### Plot 1: _________

#### Data cleanup steps specific to plot 1

These data cleaning sections are optional and depend on if you have some data cleaning steps specific to a particular plot

```{r}

```


#### Final Plot 1

```{r}

```


### Plot 2: _________

### Plot 3: ___________

Add more plot sections as needed. Each project should have at least 3 plots, but talk to me if you have fewer than 3.

### Plot 4: ___________ 

